---
title: "OLAH DATA"
author: "Amelinda Siwi Rahmawati"
date: "2023-03-01"
output: word_document
---

```Grafik Return
```{r}
library(readxl)
GOOG <- read_excel("GOOG.xlsx")
View(GOOG)

return <- GOOG$Return

plot(return, type="l", col="DARK GREEN", main="Grafik Return Saham GOOG", xlab="Date", ylab="Return")
```

```Uji Normalitas
``Dugaan dengan histogram
```{r}
par(mfrow=c(1,1))
hist(return, probability = TRUE, main = "Histogram Return Saham GOOG")
lines(density(return), col = "red")
```
``Dugaaan dengan Q-Q plot
```{r}
par(mfrow=c(1,1))
qqnorm(return, main = "Q-Q Plot Return Saham GOOG")
qqline(return)
```
``Uji KS
```{r}
library(nortest)
lillie.test(return)
```

```Metode BS
``PACKAGE
```{r}
library(OptionPricing)
BS_EC(T = 1, K = 140, r = 0.0025, sigma = 0.387443624 , S0 = 145)
BS_EP(T = 1, K = 150, r = 0.0025, sigma = 0.387443624 , S0 = 145)
```
``TANPA PACKAGE
```{r}
black_scholes<- function(S0, K, T, r, sigma, type){
  d1 <- (log(S0/K)+(r+sigma^2/2)*T)/(sigma*sqrt(T))
  d2 <- d1-sigma*sqrt(T)
  c <- S0*pnorm(d1)-K*exp(-r*T)*pnorm(d2)
  p <- K*exp(-r*T)*pnorm(-d2)-S0*pnorm(-d1)
  if(type == "call")
    return(c)
  else if (type == "put")
    return(p)
}

call_option <- black_scholes(145, 140, 1, 0.0025, 0.387443624, "call"); call_option
put_option <- black_scholes(145, 150, 1, 0.0025, 0.387443624, "put"); put_option
```

```Metode Implisit
```{r}
fdm <- function(S0, K, M, N, T, r, v, type){
  Smax = 300
  deltas = Smax/M
  deltat = T/N
  j = (0:M)
  aj = 0.5*deltat*(r*j - v*v*j^2)
  bj = 1 + deltat*v*v*j^2 + r*deltat
  cj = -0.5*deltat*(r*j - v*v*j^2)
  ajj = aj[3:M]
  bjj = bj[2:M]
  cjj = cj[2:(M-1)]
  td = triDiag2S(bjj, cjj, ajj, r = M-1)
  invtd = solve(td)
  
  vec_S = j[2:M]*deltas
  position = match(S, vec_S)
  
  if (type == "call"){
    vec_k = c()
    for (i in 1:(M-2)){
      vec_k = c(vec_k, 0)
    }
    vec_k = c(vec_k, -cj[M]*K)
    mat_k = matrix(vec_k)
    
    fc = c()
    for (i in 1:(M-1)){
      xc = max((i*deltas)-K, 0)
      fc = c(fc, xc)
    }
    for (i in 1:(N-waktu)){
      fc1 = fc + mat_k
      fc_2 = invtd %% fc1
      fc = fc_2
    }
    return(fc[position])
  } else{
    vec_k = c(-aj[2]*K)
    for (i in 1:(M-2)){
      vec_k = c(vec_k, 0)
    }
    mat_k = matrix(vec_k)
    fp = c()
    for (i in 1:(M-1)){
      xp = max(K - (i*deltas), 0)
      fp = c(fp, xp)
    }
    for (i in 1:(N-waktu)){
      fp1 = fp + mat_k
      fp2 = invtd %% fp1
      fp = fp2
    }
    return(fp[position])
  }
}

fdm(145, 140, 600, 500, 1, 0.0025, 0.387443624, "call")
```

